% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt
\input{header}

\title{Introduction to Stat for DS Groupwork-Based Assignment 2 \\ Constructive Feedback for Team Members}
% 
% 
\author{Durham Student ID: \textbf{001102553}, IT account: \textbf{bjsn39}}
\begin{document}
\maketitle
% 
% 
% 
\section{Memeber 10A}
% 
% 
\paragraph{An absolutely excellent teammate, and I hope to be paired with him again in future courses! He excelled in both mathematical knowledge and R programming techniques, providing comprehensive support for learning in the statistics course. In weekly workshops and our recent mini-report, he offered tremendous assistance. As a newcomer to the UK, I sometimes struggled to understand a phrase or two in class, and he was always there to help clarify for me. In the group report, he was the one who initially crafted the R code framework, and with his extensive geographical knowledge, he identified errors in the corresponding continents for two countries in the dataset. During data analysis, he put forth many constructive suggestions, such as advocating for regional analysis by splitting the continent data.}
\paragraph{It's challenging to pinpoint any weaknesses in his contributions. If there were any, it might be a slight need for attention to punctuality (despite punctuality is a common problem in our group). Although our discussions were spontaneous, it's advisable to be mindful of time during group meetings.}
% 
% 
\section{Memeber 10B}
% 
\paragraph{I believe he has the capability and technical skills to enhance our project even further. He is exceptionally warm and friendly, adept at socializing, and enjoys chatting with everyone after workshops, actively participating in almost every group discussion. According to other classmates, he also has a background in data science during his undergraduate studies, suggesting strong programming skills.}
% 
% 
\paragraph{However, I hope in the future he will be more proactive in attending workshops and engaging with courses on ultra. As a fellow student in the STEM field, I believe that the content of ISDS differs significantly from the statistical theory learned in our undergraduate studies. I hope he can fill in these knowledge gaps. Otherwise, as was the case when creating the slides for our group presentation, he might struggle to provide constructive feedback, spending just a few lines of text in the "Future Work" section the entire afternoon. I trust that he won't squander his talents in the field of data science in the future, and make more output in our recent mini-report as well.}
% 
\section{Memeber 10D}
% 
\paragraph{As the only female member in the team, her experience as a journal editor has endowed her with excellent aesthetic literacy. Particularly noteworthy is her contribution to our group presentation, where many beautifully crafted images are attributed to her. Despite initial disagreements on the data introduction section of our slides, she actively embraced my suggestions. Additionally, her conscientious approach to group assignments has left a lasting impression on me. Not only did she efficiently complete her assigned tasks, but she also provided us with a script for the spoken content during video production, seeking our feedback. It's truly an honor to have a teammate like her.}
% 
\paragraph{However, I've observed that she has encountered challenges in R programming, resulting in a lower profile during workshops and group assignments. I hope she can prepare for workshops diligently beforehand and even attempt to write code soon after the workshop is released. This way, she can engage in discussions with team members during class and contribute constructive suggestions for further improving our reports.}
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
\end{document}
